---
title: "simpleRegress"
author: "Addler Fuller"
date: "Summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model WEIGHT ~ NECK  this is an example  

```{r}
simp <- lm(WEIGHT~NECK,data=bears)
plot(WEIGHT~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

## Model WEIGHT ~ AGE  this is an example  

```{r}
simp <- lm(WEIGHT~AGE,data=bears)
plot(WEIGHT~AGE,data=bears)
abline(simp)
summary.lm(simp)
```


## Compare all models that predict WEIGHT other than NECK. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 


The summary for all the plots

For the Neck: The RSE was 43.91, but the Adjusted R-squared is 0.87

For the Age: The RSE was 81.47, but the Adjusted R-squared is 0.5526
